(Working Title) Stellar and Planetary Properties of \KT\ \Ci\ Candidates and Validation of \Nvalidated\ Systems, (Including a Planet Receiving Earth-like Insolation?)

### 2015-03-06 ms.tex
tdm grant added
tdm edits

\newcommand{\Nfp}{$X$}
\newcommand{\Nvalidated}{$Y$}
\newcommand{\Nlimbo}{$Z$}

@@

\title{(Working Title) Stellar and Planetary Properties of \KT\ \Ci\
Candidates and Confirmation of $N$ Systems, (Including a Planet Receiving 
Earth-like Insolation?)}

\author{
% The Heavy Lifters
Benjamin T. Montet\altaffilmark{1,2}, 
Daniel Foreman-Mackey\altaffilmark{3},
Timothy D. Morton,
% The Benefactors
John Asher Johnson,
David W. Hogg,
% The Observers
% (ranked by integration time x collecting area)
Brendan P. Bowler,
David W. Latham,
Allyson Bieryla,
Andrew W. Mann,
And Any TRES Team Members We Should Add
}

@@

\altaffiltext{1}{Cahill Center for Astronomy and Astrophysics, California Institute of Technology, 1200 E. California Blvd., MC 249-17, Pasadena, CA 91106, USA}
\altaffiltext{2}{Harvard-Smithsonian Center for Astrophysics, 60 Garden
Street, Cambridge, MA 02138, USA}
\altaffiltext{3}{Department of Astronomy, University of Michigan, Ann Arbor, MI 48109, USA}

@@

\begin{abstract}
Recently, \paperit{} presented a list of 36 planet candidates orbiting
31 stars in \KT\ \Ci. 
In this paper, we present stellar and planetary properties for all systems.
We combine archival imaging, ground-based seeing limited survey data, and
adaptive optics imaging with a detailed transit analysis scheme to confirm 
\btmtodo{Nconfirm} as planets and \btmtodo{NFP} as false positives
at the \btmtodo{confidence} level.
Of particular interest is EPIC 201912552, a bright (K=8.9) M2 dwarf
hosting a \anytodo{Radius} planet with $T_{eq} = 275 \pm 15$ K and an 
orbital period of 33 days.
\anytodo{Anything we should add?}
\end{abstract}

@@

\citet{Morton12} described an automated method to calculate the
probability that a planet candidate might be caused by an
astrophysical false positive.  This method uses population simulations
of false positive scenarios and true transiting planets to quantify
the typical shape of each, and combines prior information about the
populations of field stars and multiple star systems in order to
determine the probability that the observed signal may be a false
positive.  Similar in spirit to other published methods of
probabilistic validation, such as Blender \citep{} and PASTIS
\citep{}, it has the advantage of being computationally less demanding
and fully automated, and thus easily applied in batch to a large
number of candidates.

In this work, we use
\texttt{vespa}\footnote{\url{http://github.com/timothydmorton/vespa}},
a new implementation of the \citet{Morton12} procedure, to calculate
the false positive probabilities of each of these K2 candidates,
supplemented in a few cases by high-resolution imaging, where
available.  Table \ref{table:FPP} summarizes the results of these
calculations, presenting the relative probability for each candidate
to be caused by any of three false positive scenarios: an undiluted
eclipsing binary (EB), a hierarchical triple eclipsing binary (HEB),
and a chance-aligned background(/foreground) eclipsing binary (BEB).
We find that \Nfp\ of the presented candidates have false positive
probabilities (FPPs) $>$80\%; these we consider to be likely false
positives.  On the other hand, we find that \Nvalidated\ candidates
have FPP $<$ 1\%; these we consider to be validated planets.  The
remaining \Nlimbo\ candidates have FPPs neither high enough to discard
nor low enough to securely validate.

@@

>>>>

\newcommand{\Nfp}{4}
\newcommand{\Nvalidated}{21}
\newcommand{\Nlimbo}{11}

@@

\title{(Working Title) Stellar and Planetary Properties of \KT\ \Ci\
Candidates and Validation of \Nvalidated\ Systems, (Including a Planet Receiving 
Earth-like Insolation?)}

\author{
% The Heavy Lifters
Benjamin T. Montet\altaffilmark{1,2}, 
Daniel Foreman-Mackey\altaffilmark{3},
Timothy D. Morton\altaffilmark{4},
% The Benefactors
John Asher Johnson,
David W. Hogg,
% The Observers
% (ranked by integration time x collecting area)
Brendan P. Bowler,
David W. Latham,
Allyson Bieryla,
Andrew W. Mann,
And Any TRES Team Members We Should Add
}

@@

\altaffiltext{1}{Cahill Center for Astronomy and Astrophysics, California Institute of Technology, 1200 E. California Blvd., MC 249-17, Pasadena, CA 91106, USA}
\altaffiltext{2}{Harvard-Smithsonian Center for Astrophysics, 60 Garden
Street, Cambridge, MA 02138, USA}
\altaffiltext{3}{Department of Astronomy, University of Michigan, Ann Arbor, MI 48109, USA}
\altaffiltext{4}{Department of Astrophysics, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}

@@

\begin{abstract}
Recently, \paperit{} presented a list of 36 planet candidates orbiting
31 stars in \KT\ \Ci. 
In this paper, we present stellar and planetary properties for all systems.
We combine archival imaging, ground-based seeing limited survey data, and
adaptive optics imaging with a detailed transit analysis scheme to confirm 
\Nvalidated\ as planets and identify \Nfp\ as likely false positives.
Of particular interest is EPIC 201912552, a bright (K=8.9) M2 dwarf
hosting a \anytodo{Radius} planet with $T_{eq} = 275 \pm 15$ K and an 
orbital period of 33 days.
\anytodo{Anything we should add?}
\end{abstract}

@@

\citet{Morton12} presented an automated method to calculate the
probability that a planet candidate might be caused by an
astrophysical false positive.  
This method uses population simulations
of false positive scenarios and true transiting planets to quantify
the typical shape of each, comparing to the observed transit shape.
It then combines this information with observationally motivated prior
assumtions about the populations of field stars, the properties of 
multiple star systems, and the occurrence rate of planets as determined
from \kep\ \citet{Fressin13}, in order to determine the probability that 
the observed signal may be a false positive.  
Similar in spirit to other published methods of
probabilistic validation, such as Blender \citep{} and PASTIS
\citep{}, it has the advantage of being computationally less demanding
and fully automated, and thus easily applied in batch to a large
number of candidates.

In this work, we use
\texttt{vespa}\footnote{\url{http://github.com/timothydmorton/vespa}},
a new implementation of the \citet{Morton12} procedure, to calculate
the false positive probabilities of each of these K2 candidates.  
While we do have follow-up observations of a number of these systems,
we do the preliminary FPP calculations without taking these into account,
relying solely on the probabilistic \texttt{vespa} analysis.

Table \ref{table:FPP} summarizes the results of these
calculations, presenting the relative probability for each candidate
to be caused by any of three false positive scenarios: an undiluted
eclipsing binary (EB), a hierarchical triple eclipsing binary (HEB),
and a chance-aligned background(/foreground) eclipsing binary (BEB).

We find that \Nfp\ of the presented candidates have false positive
probabilities (FPPs) $>$90\%; these we consider to be likely false
positives.  
On the other hand, we find that \Nvalidated\ candidates
have FPP $<$ 1\%; these we consider to be validated planets.  
The remaining \Nlimbo\ candidates have FPPs neither high enough to discard
nor low enough to securely validate.

We emphasize that t

@@

T.D.M.~is supported by the National Aeronautics and Space Administration (grant 
NNX14AE11G).
